Arrows for Parallel Computations

### 2017-12-14 paper/content/utilityFunctions.tex
minor

instance (Category p, Strong p, Choice p) => ArrowChoice p where
  left = left'
\end{code}
\caption{Profunctors as Arrows}
\footnote{for additional information on the typeclasses see: \url{https://hackage.haskell.org/package/profunctors-5.2.1/docs/Data-Profunctor.html} and \url{https://hackage.haskell.org/package/base-4.9.1.0/docs/Control-Category.html}}
\label{fig:profunctorArrow}
\end{figure}

>>>>

instance (Category p, Strong p, Choice p) => ArrowChoice p where
  left = left'
\end{code}
\caption{Profunctors as Arrows\protect\footnotemark}
\label{fig:profunctorArrow}
\end{figure}

\footnotetext{for additional information on the typeclasses used, see: \url{https://hackage.haskell.org/package/profunctors-5.2.1/docs/Data-Profunctor.html} and \url{https://hackage.haskell.org/package/base-4.9.1.0/docs/Control-Category.html}}
